Merging merges, more or less

### 2015-04-09 2015mergingmerges/section/06-Conclusion.tex
ok

In this example, if the machines for @xs'@ and @ys'@ are fused together first, the fusion will prematurely decide on an ordering of both machines: perhaps all @xs'@ will be computed followed by all @ys'@, perhaps the other way around, or maybe they will be interspersed as we wish.
Then, when this arbitrarily-ordered machine is fused with the @zip@, it will fail as the @zip@ would need to read all the @xs'@ before finding a @ys'@.
It is important to note, however, that the ordering of fusion does not affect the semantics of the result, just whether a result is found.

@@

>>>>

In this example, if the machines for @xs'@ and @ys'@ are fused together first, the fusion will prematurely decide on an ordering of both machines: perhaps all @xs'@ will be computed followed by all @ys'@, perhaps the other way around, or maybe they will be interspersed as we wish.
If the first is taken, when this arbitrarily-ordered machine is fused with the @zip@, it will fail as the @zip@ would need to read all the @xs'@ before finding a @ys'@.
It is important to note, however, that the ordering of fusion does not affect the semantics of the result, just whether a result is found.

@@

% Kahn process networks\cite{kahn1976coroutines} are a flexible and valuable abstraction\cite{vrba2009kahn}, but they 
% Our fusion system is able to handle a strict subset of Kahn process networks\cite{kahn1976coroutines}.
% which are known to be flexible\cite{vrba2009kahn}
